Defending Against Web Application Attacks: Research Approaches, Challenges and Implications

### 2015-01-15 docs/reviewers_response.txt

Reviewer 1
==========

> -The sensitivity and specificity metrics are questionable (need
> justification and relation to standard techniques), and anyway not
> used much in Table I.

That's exactly what we try to highlight in the paper. Sensitivity and
specificity should be more widely applicable, but they are not,
because not enough data is given in the original publications. In
general, as we remark in VII.A, "In many cases researchers tend not to
provide the false positive and negative results that their tools may
produce."

Concerning the usefullness of sensitivity and specicifity as metrics
per se, their use in computer security has been advocated by other
researchers as well, for example ***.

Reviewer 2
==========

> The paper essentially provides only information that is directly
> available from other publications. This applies especially to the
> categories accuracy and performance overhead, where several mechanisms
> do not provide data. The authors of the paper did not perform any
> original tests.

Please note that even if we wanted to perform original tests on the
systems we studied, or even if we wanted to validate the existing
tests, we would not be able to do so in the vast majority of cases, as
indicated in Table II; this is in fact one of our main findings, as we
explain in VII.B.

Reviewer 3
==========

> From my understanding, sensitivity and specificity could also be
> expressed in terms of conditional probability: sensitivity is the
> conditional probability that the detection mechanism flags an attack,
> given that an attack is taking place, and specificity is the
> conditional probability that the mechanism does not report an attack,
> given that no attack takes place.

Correct. We can of course add that to the power; we just thought that
it might not be necessary to explain it.

> This would help in discerning and relating these measures from and to
> the positive and negative predictive values, and also explains
> formulas (5) and (6) on page 13.

Correct, as above we can easily add the explanations.

> Moreover, the discussion seems to be confusing experiment measurements
> and abstract probabilities.
> On page 2 [actually it's on p. 5], it is stated that "sensitivity
> and specificity can be calculated on test data alone".
> On page 13, it is said that "PPV and NPV ... relate to the
> effectiveness in an actual production environment".

This is to highlight that we cannot carry out a set of measurements,
calculate sensitity and specificity, and then using the {True | False
} {Positives | Negatives} calculate the PPV and the NPV from equations
3 and 4 directly. One has to go instead through equations 5 and 6.

> Obviously, any measurement of true and false positives and negatives
> on test data can be skewed, if the test data is skewed.
> Hence, if the sensitivity and specificity are measured using tests
> that do not relate to "the production environment", the calculated
> values are meaningless.

Definitely, we can highlight that.

> Yet this holds true for all four measures; it is simply related to the
> way they are estimated.
> The advantage of PPV and NPV is that they answer the question of
> "given a detection result, how much can you trust it?", which is more
> interesting in the "production environment".
>
> This part of the paper should be revised to give a clearer picture.

Taking into account all your related comments, we will do that, taking
care not to go through the paper length limits. The gist is that,
indeed, PPV and NPV answer the question you state; it is not always
possible to get data for them (since we may not know the prevalence),
but it may worth to try and get it, or this could be a new research
direction. Of course, if we do have such data, it is a way to
operationalize the protection a system provides.

The validity of test data is in fact important independently of
sensitivity and specificity; skewed test data will give a wrong
picture anyway, even if nobody bothers to calculate sensitivity and
specificity. We do not know in the papers we studies whether test data
were skewed. We do find, however, that: more tests could have been
carried out (cf. Table I and VII.A ) and the means to conduct tests should be
made available to third parties (cf. Table II and VII.B).

Reviewer 4
==========

> Similarly, the demand on taking the prevalence into consideration when
> evaluating false positives and false negatives may be an undue burden
> on security researchers, who would have a hard time collecting these
> probabilities. On the other hand, this might call for a common attack
> dataset.

That is why we state, in p. 13, that "With this in mind it may be
unfair to ask of researchers to provide PPV and NPV values for
their mechanisms---in fact, we see that nobody does." In the following
paragraph (last paragraph of first column in p. 13) we explore what
this would require. We can make it more clear.

### 2015-01-15 docs/rebuttal.txt

We can update our model to show where the language-level and web
framework-level protection mechanisms detect an attack. In particular
we can show that this is done at the application level within the server.

The comments concerning Firing Range, XCS attacks, scriptless attacks
and attacks that involve plug-ins are totally valid and we are
planning to address them in the next version of the paper.

- Reviewer 2:

# dimitro: maybe we need to mention that we cover only mechanisms
# that have been presented in a research publication as a general
# remark in the beginning of our response.

We tried to equally cover every mechanism and then as the paper
progresses we highlight the reasons why a mechanism may be widely
used or not. In our conclusion section, we particularly mention
that CSP is one of the few mechanisms that contrary to other approaches,
has been presented in a research publication and at the same time
is widely used. Furthermore, it is true that if a programmer uses
secure coding practices (for instance prepared statements) then
a mechanism that counters SQLIAs is not necessarily needed.
However, as we mention in the paper, programmers are not always
that careful and this is why protection mechanisms like SQLrand
have been proposed in the first place.

In the description of our model, we state that there are two
ways to initiate the majority of the presented attacks.
In both cases, the first steps will result to the same path.
To distinguish these first step we use the 1 - 1.1 notation.
The point concerning the PHP injection attack is valid. In general,
we tried to illustrate the most known web injection attacks in our
model. Still, with can easily incorporate such an attack in our model
with minor modifications (the same applies to POI attacks as we
already mention in the paper).

Finally, our model covers attacks that utilize DSL languages in general
(including SQL, XPath etc.), while in our categorization there is
more than one countermeasure that protects from XPath injection attacks.

### 2015-01-15 docs/rebuttal.txt

In the description of our model, we state that there are two
ways to initiate the majority of the presented attacks.
In both cases, the first steps will result to the same path.
To distinguish these first step we use the 1 - 1.1 notation.
The point concerning the PHP injection attack is valid. In general,
we tried to illustrate the most known web injection attacks in our
model. Still, with can easily incorporate such an attack in our model
with minor modifications (the same applies to POI attacks as we
already mention in the paper).

Finally, our model covers attacks that utilize DSL languages in general
(including SQL, XPath etc.), while in our categorization there is
more than one countermeasure that protects from XPath injection attacks.

- Reviewer 3:

As we mention in the introduction of our paper, we did not cover static
analysis tools that detect vulnerabilities that lead to the covered attacks
because there is a corresponding survey by that does exactly that [14].

# dimitro: here we go again.

As we also mentioned to the previous responses, we did not include
in our categorization, mechanisms that have not been presented in
a research paper. However, Caja is a very important mechanism
and this is why we reference it in our paper and particularly as
a framework that is widely used.

We do agree with the comment on the "ease of use" dimension and we will
address it in our next revision. Also, the comment about the EiQ is
correct: it is DBAL. Finally, we will update our SQL injection
example to make it clearer.

### 2015-01-15 docs/rebuttal_merged.txt

- General Remarks:

We want to thank the reviewers for their meaningful comments.

- Reviewer 1:

# --- Panos ---

> -The sensitivity and specificity metrics are questionable (need
> justification and relation to standard techniques), and anyway not
> used much in Table I.

That's exactly what we try to highlight in the paper. Sensitivity and
specificity should be more widely applicable, but they are not,
because not enough data is given in the original publications. In
general, as we remark in VII.A, "In many cases researchers tend not to
provide the false positive and negative results that their tools may
produce."

Concerning the usefullness of sensitivity and specicifity as metrics
per se, their use in computer security has been advocated by other
researchers as well, for example ***.

# --- Dimitro ---

@@

We can update our model to show where the language-level and web
framework-level protection mechanisms detect an attack. In particular
we can show that this is done at the application level within the server.

The comments concerning Firing Range, XCS attacks, scriptless attacks
and attacks that involve plug-ins are totally valid and we are
planning to address them in the next version of the paper.

- Reviewer 2:

--- Panos ---

> The paper essentially provides only information that is directly
> available from other publications. This applies especially to the
> categories accuracy and performance overhead, where several mechanisms
> do not provide data. The authors of the paper did not perform any
> original tests.

Please note that even if we wanted to perform original tests on the
systems we studied, or even if we wanted to validate the existing
tests, we would not be able to do so in the vast majority of cases, as
indicated in Table II; this is in fact one of our main findings, as we
explain in VII.B.

--- Dimitro ---

@@

# dimitro: here we go again.

As we also mentioned to the previous responses, we did not include
in our categorization, mechanisms that have not been presented in
a research paper. However, Caja is a very important mechanism
and this is why we reference it in our paper and particularly as
a framework that is widely used.

We do agree with the comment on the "ease of use" dimension and we will
address it in our next revision. Also, the comment about the EiQ is
correct: it is DBAL. Finally, we will update our SQL injection
example to make it clearer.

--- Panos ----

> From my understanding, sensitivity and specificity could also be
> expressed in terms of conditional probability: sensitivity is the
> conditional probability that the detection mechanism flags an attack,
> given that an attack is taking place, and specificity is the
> conditional probability that the mechanism does not report an attack,
> given that no attack takes place.

Correct. We can of course add that to the power; we just thought that
it might not be necessary to explain it.

> This would help in discerning and relating these measures from and to
> the positive and negative predictive values, and also explains
> formulas (5) and (6) on page 13.

Correct, as above we can easily add the explanations.

> Moreover, the discussion seems to be confusing experiment measurements
> and abstract probabilities.
> On page 2 [actually it's on p. 5], it is stated that "sensitivity
> and specificity can be calculated on test data alone".
> On page 13, it is said that "PPV and NPV ... relate to the
> effectiveness in an actual production environment".

This is to highlight that we cannot carry out a set of measurements,
calculate sensitity and specificity, and then using the {True | False
} {Positives | Negatives} calculate the PPV and the NPV from equations
3 and 4 directly. One has to go instead through equations 5 and 6.

> Obviously, any measurement of true and false positives and negatives
> on test data can be skewed, if the test data is skewed.
> Hence, if the sensitivity and specificity are measured using tests
> that do not relate to "the production environment", the calculated
> values are meaningless.

Definitely, we can highlight that.

> Yet this holds true for all four measures; it is simply related to the
> way they are estimated.
> The advantage of PPV and NPV is that they answer the question of
> "given a detection result, how much can you trust it?", which is more
> interesting in the "production environment".
>
> This part of the paper should be revised to give a clearer picture.

Taking into account all your related comments, we will do that, taking
care not to go through the paper length limits. The gist is that,
indeed, PPV and NPV answer the question you state; it is not always
possible to get data for them (since we may not know the prevalence),
but it may worth to try and get it, or this could be a new research
direction. Of course, if we do have such data, it is a way to
operationalize the protection a system provides.

The validity of test data is in fact important independently of
sensitivity and specificity; skewed test data will give a wrong
picture anyway, even if nobody bothers to calculate sensitivity and
specificity. We do not know in the papers we studies whether test data
were skewed. We do find, however, that: more tests could have been
carried out (cf. Table I and VII.A ) and the means to conduct tests should be
made available to third parties (cf. Table II and VII.B).

@@

- Reviewer 4:

--- Dimitro ---

We need to make clear that we do not want to criticize the lack of testing
in etiological mechanisms. We try to investigate the reason why such mechanisms
are not widely used and we suggest that this is one reason.

--- Panos ---

> Similarly, the demand on taking the prevalence into consideration when
> evaluating false positives and false negatives may be an undue burden
> on security researchers, who would have a hard time collecting these
> probabilities. On the other hand, this might call for a common attack
> dataset.

That is why we state, in p. 13, that "With this in mind it may be
unfair to ask of researchers to provide PPV and NPV values for
their mechanisms---in fact, we see that nobody does." In the following
paragraph (last paragraph of first column in p. 13) we explore what
this would require. We can make it more clear.

### 2015-01-16 docs/rebuttal_merged.txt

We want to thank the reviewers for their meaningful comments.

As a general remark we need to say that as we state in the
paper, we did not include in our categorization mechanisms that
have not been presented in a research paper. However, Caja
is an important mechanism and this is why we reference it
as a framework that is widely used. Also, we are aware
that some of the presented approaches utilize
either static or dynamic analysis. As we explain in the paper though,
we dismiss static and dynamic approaches that identify
vulnerabilities that may lead to injection attacks
(there is a corresponding survey that covers this area [14])
and cover protection mechanisms that counter such attacks when
they take place.

Rev1:

Concerning the skepticism on the sensitivity and specificity metrics
we need to mention that these metrics should be more widely applicable,
but they are not, because not enough data is given in the
original publications as we remark in VII.A. Also, the
usefulness of such metrics in computer security has been advocated
by other researchers as well, as we discuss in the same Section.

@@

It is true that there are to many N/As in both Tables and especially in
Table II. However, we believe that issues concerning code availability and
accuracy testing are instantly identified by a casual reader.

We agree that we should (and we will) incorporate the term "injection"
into the paper's title.

We can include ADsafe etc. in the paper in the way we
include Google Caja. Also, we will include FlowFox and
JSand (both have >20 citations --- our threshold),
and the paper presenting IFC in WebKit's
JavaScript Bytecode (which is a recent paper presented in a
respected venue) in the paper. We could also include AdSentry,
Contego and JSFlow too, but they do not reach our citation threshold.

We agree that using "security" as a term for one of our dimensions
may be misleading since it is a generic term and in this case
we need to make it more specific.

The point about the minimalism of the security discussion is actually
pretty good and we will try to enrich this part. A first attempt
would be to say that approaches that provide systematic
arguments on why their designs are secure, are not as
by-passable as the approaches coming from the other
category.

We can update our model to show where the language and web
framework-level protection mechanisms detect an attack
(the point would be at the application level within the server).

The comments concerning Firing Range, XCS attacks, scriptless attacks
and attacks that involve plug-ins are valid and we are
planning to address them.

Rev2:

Please note that even if we wanted to perform original tests on the
systems we studied, or even if we wanted to validate the existing
tests, we would not be able to do so in the vast majority of cases, as
indicated in Table II; this is in fact one of our main findings, as we
explain in VII.B.

We tried to equally cover every mechanism and then as the paper
progresses we highlight the reasons why a mechanism may be widely
used or not. In our conclusion section, we particularly mention
that CSP is one of the few mechanisms that contrary to others,
has been presented in a research publication and at the same time
is widely used. Furthermore, it is true that if a programmer uses
secure coding practices like prepared statements, then
a mechanism that counters SQLIAs is not necessarily needed.
However, as we mention in the paper, programmers are not always
that careful and this is why protection mechanisms like SQLrand
have been proposed in the first place.

In our model description, we state that there are two
ways to initiate the majority of the presented attacks.
In both cases, the first steps will result to the same path.
To distinguish these first steps we use the 1 - 1.1 notation.
The point concerning the PHP injection attack is valid. In general,
we tried to illustrate the most known injection attacks in our
model. Still, we can incorporate such an attack in our model
with minor modifications.

Finally, our model covers attacks that utilize DSL languages in general,
while in our categorization there is more than one countermeasures that
protects from XPath injection attacks.

Rev3:

@@

We do agree with the comment on the "ease of use" dimension and we will
address it in our next revision. Also, the comment about the EiQ is
correct: it is DBAL. Finally, we will update our SQL injection
example to make it clearer.

We fully agree with the the fact that the sensitivity and specificity
metrics could also be expressed in terms of conditional probability
and we can add that to the power.

With our discussion in page 2 and 13 respectively we
want to highlight that we cannot carry out a set of measurements,
calculate sensitivity and specificity, and then using the {True | False
} {Positives | Negatives} calculate the PPV and the NPV from equations
3 and 4 directly. One has to go instead through equations 5 and 6.

Taking into account all the related comments, we will
update the paper to highlight the advantages of PPV and NPV.
The gist is that, indeed, PPV and NPV answer the question
about trusting a detection result; it is not always
possible to get data for them (since we may not know the prevalence),
but it may worth to try and get it, or this could be a new research
direction. Of course, if we do have such data, it is a way to
operationalize the protection a system provides.

The comment on the skewed data is valid and we can
elaborate on it more. The validity of test data is in fact
important independently of sensitivity and specificity;
skewed test data will give a wrong picture anyway, even if nobody
bothers to calculate the metrics. We do not know in the
papers we studied whether test data were skewed. We do find,
however, that: more tests could have been
carried out (Table I and VII.A) and the means to conduct tests should be
made available to third parties (Table II and VII.B).

Rev4:

We need to make clear that we do not want to criticize the lack of testing
in etiological mechanisms. In fact, we try to investigate
the reason why such mechanisms are not widely used and we suggest
that this is one reason.

Regarding the comment about demanding prevalence, we need to say that
as we state in the paper, it may be unfair to ask of
researchers to provide PPV and NPV values for
their mechanisms---in fact, nobody does. In the
last paragraph of first column in p.13 we explore what
this would require. We can elaborate more.

### 2015-01-16 docs/rebuttal_merged.txt

We thank the reviewers for their insightful comments.

Overall, we did not consider mechanisms that
have not been presented in research papers. We mention Caja
due to its importance and popularity.  Also, although
some of the presented works use
static/dynamic analysis, we do not
consider the broader area of static/dynamic analysis for
vulnerability detection (another paper covers that area [14]),
but focus only on protections against attacks
that might exploit such vulnerabilities.

@@

Rev1:

Sensitivity and specificity should be more widely applicable,
but not enough data is given in the
original publications, as mentioned in VII.A. The
usefulness of such metrics in computer security has been advocated
by other researchers as mentioned in the same section.

It is true that there are too many N/As, especially
Table II, but this actually highlights the issues regarding
code availability and accuracy testing.

We agree that "injection" should be part of the title,
and we will incorporate it.

We will include FlowFox and JSand (both have >20 citations),
the paper presenting IFC in WebKit's
JavaScript Bytecode (a recent paper)
and discuss ADsafe etc. in the same way as Google Caja.
AdSentry, Contego, and JSFlow 
do not reach our citation threshold.

We agree that using "security" as a dimension
is misleading---we use it in the sense of "bypassability", which is 
orthogonal to "accuracy". We will replace it with a more specific term.

We fully agree with the point about the minimalism of the security discussion,
and will try to enrich this part. For instance,
approaches that provide systematic
arguments on why their designs are secure, are not as
"bypassable" as heuristic/threshold-based approaches.

@@

We can update our model to show where the language and web
framework-level protection mechanisms detect an attack
(the point would be at the application level within the server).

The comments about Firing Range, XCS attacks, scriptless attacks,
and attacks that involve plug-ins are valid and we will address them.

@@

Rev2:

The lack of code availability for most systems 
makes performing original tests challenging.
This is in fact one of our findings, as we explain in VII.B.

We attempted to equally cover every mechanism and then
highlight the reasons why a mechanism may be widely
used or not. In our conclusion section, we particularly mention
that CSP is one of the few that 
has been published and is widely used.
It is true that if a programmer uses
secure coding practices like prepared statements, then
SQLi protections are not required.
However, best programming practices are not always followed,
and this motivates proposals like SQLrand,
which might be easier to retrofit in existing code bases.

We use the 1/1.1 notation to distinguish some shared states by the two main ways
attacks in our model can be initiated---we will explore a more clear representation.
The point regarding PHP injection attacks is valid.
We tried to capture the most known injection attacks,
and we will incorporate this attack with a few minor modifications to the model.
Our model covers attacks that utilize DSL languages in general,
and in our categorization there are more than one countermeasures that
protect from XPath injection attacks.

@@

Rev3:

We agree with the comment on the "ease of use" dimension and we will
address it. Also, the comment about the EiQ is
correct: it is DBAL. We will make our SQLi example clearer.

We fully agree that sensitivity and specificity
could be expressed in terms of a conditional probability---we will
include this in the paper.

Our discussion in pages 2 and 13 respectively
highlights that we cannot carry out a set of measurements,
calculate sensitivity and specificity, and then using {True|False}
{Positives|Negatives} calculate PPV and NPV from equations
3 and 4 directly. One has to go instead through equations 5 and 6.

Taking into account all related comments, we will
highlight the advantages of PPV and NPV.
The gist is that, indeed, PPV and NPV answer the question
about trusting a detection result; it is not always
possible to get data for them (since we may not know the prevalence),
but it may be worth it to try and get it, or this could be a new research
direction. Of course, if we do have such data, it is a way to
operationalize the protection a system provides.

@@

The comment on the skewed data is valid and we can
elaborate on it more. The validity of test data is in fact
important independently of sensitivity and specificity;
skewed test data will give a wrong picture anyway, even if nobody
bothers to calculate the metrics. We do not know in the
papers we studied whether test data were skewed. We do find,
however, that: more tests could have been
carried out (Table I and VII.A) and the means to conduct tests should be
made available to third parties (Table II and VII.B).

Rev4:

We do not intend to criticize the lack of testing
in etiological mechanisms. We attempt to 
explore why such mechanisms are not widely used, and suggest
that this is one reason.

Regarding the comment about demanding prevalence,
it may be unfair to ask of researchers to provide PPV and NPV values for
their mechanisms---in fact, nobody does. In the
p.13 we explore what this would require---we will elaborate more.

Finally, we will discuss more incentives
that the community could provide to improve code availability.

### 2015-01-16 docs/rebuttal_merged.txt

Overall, we did not consider mechanisms that
have not been presented in research papers. We mention Caja
due to its importance and popularity.  Also, although
some of the presented works use
static/dynamic analysis, we do not
consider the broader area of static/dynamic analysis for
vulnerability detection (another paper covers that area [14]),
but focus only on protections against attacks
that might exploit such vulnerabilities.

Rev1:

Sensitivity and specificity should be more widely applicable,
but not enough data is given in the
original publications, as mentioned in VII.A. The
usefulness of such metrics in computer security has been advocated
by other researchers as mentioned in the same section.

There are too many N/As, especially Table II, but this actually
highlights the issues regarding code availability and accuracy
testing.

@@

We agree that "injection" should be part of the title,
and we will incorporate it.

We will include FlowFox and JSand (both have >20 citations),
the paper presenting IFC in WebKit's
JavaScript Bytecode (a recent paper)
and discuss ADsafe etc. in the same way as Google Caja.
AdSentry, Contego, and JSFlow 
do not reach our citation threshold.

We agree that using "security" as a dimension
is misleading---we use it in the sense of "bypassability", which is 
orthogonal to "accuracy". We will replace it with a more specific term.

We fully agree about the minimalism of the security discussion, and
will try to enrich this part. For instance, approaches that provide
systematic arguments on why their designs are secure, are not as
"bypassable" as heuristic/threshold-based approaches.

@@

Rev2:

The lack of code availability for most systems makes performing
original tests challenging. This is in fact one of our findings, as we
explain in VII.B.

We attempted to equally cover every mechanism and then
highlight the reasons why a mechanism may be widely
used or not. In our conclusion section, we particularly mention
that CSP is one of the few that 
has been published and is widely used.
It is true that if a programmer uses
secure coding practices like prepared statements, then
SQLi protections are not required.
However, best programming practices are not always followed,
and this motivates proposals like SQLrand,
which might be easier to retrofit in existing code bases.

We use the 1/1.1 notation to distinguish some shared states by the two
main ways attacks in our model can be initiated---we will explore a
clearer representation. The point regarding PHP injection attacks
is valid. We tried to capture the most known injection attacks, and we
will incorporate this attack with a few minor modifications to the
model. Our model covers attacks that utilize DSL languages in general,
and in our categorization there are more than one countermeasures that
protect from XPath injection attacks.

@@

Rev3:

We agree with the comment on the "ease of use" dimension and we will
address it. Also, the comment about the EiQ is
correct: it is DBAL. We will make our SQLi example clearer.

Of course sensitivity and specificity could be expressed in terms of a
conditional probability---we will include this in the paper.

@@

Our discussion in pages 2 and 13 respectively highlights that we
cannot carry out a set of measurements, calculate sensitivity and
specificity, and then using {True|False} {Positives|Negatives}
calculate PPV and NPV from equations 3 and 4 directly. One has to go
instead through equations 5 and 6.

We will expand on the advantages of PPV and NPV. PPV and NPV answer
the question about trusting a detection result; however,it is not
always possible to get data for them as we indicate in p. 13.

The comment on the skewed data is valid. The validity of test data is
important independently of sensitivity and specificity. We do not know
in the papers we studied whether test data were skewed. We do find,
however, that: more tests could have been carried out (Table I and
VII.A) and the means to conduct tests should be made available to
third parties (Table II and VII.B).

@@

Rev4:

We do not intend to criticize the lack of testing
in etiological mechanisms. We attempt to 
explore why such mechanisms are not widely used, and suggest
that this is one reason.

Regarding the comment about demanding prevalence, it may be unfair to
ask of researchers to provide PPV and NPV values for their mechanisms.
In the p.13 we explore what this would require---we will elaborate
more.

### 2015-01-16 docs/rebuttal_merged.txt

We thank the reviewers for their insightful comments.

Overall, we didn't consider mechanisms that
haven't been presented in research papers. We mention Caja
due to its importance and popularity.  Also, although
some of the presented works use
static/dynamic analysis, we don't
consider the broader area of static/dynamic analysis for
vulnerability detection (another paper covers that area [14]),
but focus only on protections against attacks
that might exploit such vulnerabilities.

In general, we will update our text and our model
to address the various issues indicated by the
the reviewers like the paper's title,
the point where language protection mechanisms detect an attack,
the "ease of use" dimension, the SQLi example,
and the code availability discussion.

@@

Rev1:

Sensitivity and specificity should be more widely applicable,
but not enough data is given in the
original publications (see VII.A).
The usefulness of such metrics in computer security
has been advocated by other researchers too, such as
Pfleeger and Pfleeger (Analyzing Computer Security:
A Threat/Vulnerability/Countermeasure Approach,
Prentice Hall, 2011); we’ll add the citations.

@@

There are too many N/As, especially Table II, but this actually
highlights the issues regarding code availability and accuracy
testing.

We will include FlowFox and JSand (both have >20 citations),
the paper presenting IFC in WebKit's
JavaScript Bytecode (a recent paper)
and discuss ADsafe etc. in the same way as Caja.
AdSentry, Contego, and JSFlow 
don't reach our citation threshold.

@@

We agree that using "security" as a dimension
is misleading---we use it in the sense of "bypassability", which is 
orthogonal to "accuracy". We will replace it with a more specific term.

We fully agree about the minimalism of the security discussion, and
will try to enrich this part. For instance, approaches that provide
systematic arguments on why their designs are secure, aren't as
"bypassable" as heuristic/threshold-based approaches.

@@

Rev2:

The lack of code availability for most systems makes performing
original tests challenging, which is one of our findings, as we
explain in VII.B.

We attempted to equally cover every mechanism and then
highlight the reasons why a mechanism may be widely
used or not. In our conclusion section, we particularly mention
that CSP is one of the few that 
has been published and is widely used.
It is true that if programmers use
secure coding practices like prepared statements, then
SQLi protections aren't required.
However, best programming practices aren't always followed,
and this motivates proposals like SQLrand,
which might be easier to retrofit in existing code bases.

We use the 1/1.1 notation to distinguish some shared states by the two
main ways attacks in our model can be initiated---we'll explore a
clearer representation. The point regarding PHP injection attacks
is valid. We tried to capture the most known injection attacks, and we
will incorporate this attack with a few minor modifications to the
model. Our model covers attacks that utilize DSL languages in general,
and in our categorization there are more than one countermeasures that
protect from XPathi.

@@

Rev3:

Of course sensitivity and specificity could be expressed in terms of a
conditional probability---we will include this in the paper.

Our discussion in pages 2 and 13 highlights that we
cannot carry out a set of measurements, calculate sensitivity and
specificity, and then using {True|False} {Positives|Negatives}
calculate PPV and NPV from equations 3 and 4 directly. One has to go
instead through equations 5 and 6.

We will expand on the advantages of PPV and NPV. PPV and NPV answer
the question about trusting a detection result; however,it isn't
always possible to get data for them as we indicate in p. 13.

The comment on the skewed data is valid. The validity of test data is
important independently of sensitivity and specificity. We don't know
in the papers we studied whether test data were skewed. We do find,
however, that: more tests could have been carried out (Table I and
VII.A) and the means to conduct tests should be made available to
third parties (Table II and VII.B).

@@

Rev4:

We don't intend to criticize the lack of testing
in etiological mechanisms. We attempt to 
explore why such mechanisms aren't widely used, and suggest
that this is one reason.

### 2015-01-16 docs/rebuttal_merged.txt

We thank the reviewers for their insightful comments.

Overall, we didn't consider mechanisms that
haven't been presented in research papers. We mention Caja
due to its importance.

Although some of the presented works use
static/dynamic analysis, we don't
consider the broader area of static/dynamic analysis for
vulnerability detection (another paper covers that area [14]),
but focus only on protections against attacks
that exploit such vulnerabilities.

We will update our paper
to address the issues indicated by the
the reviewers, i.e. the title,
the point where language protection mechanisms detect an attack,
the "ease of use" dimension, the SQLi example,
the fact that we fail to capture PHP injection in our model,
the 1/1.1 notation in our model, and
the code availability discussion.

@@

Rev1:

Sensitivity and specificity should be more widely applicable,
but not enough data is given in the publications (see VII.A).
The usefulness of such metrics in computer security
has been advocated by other researchers too, i.e.
Pfleeger and Pfleeger (Analyzing Computer Security:
A Threat/Vulnerability/Countermeasure Approach,
Prentice Hall, 2011); we’ll add the citations.

@@

There are too many N/As, especially Table II, but this actually
highlights the issues regarding code availability and accuracy
testing.

We will include FlowFox and JSand (both have >20 citations),
the paper presenting IFC in WebKit's
JavaScript Bytecode (a recent paper)
and discuss ADsafe etc. in the same way as Caja.
AdSentry, Contego, and JSFlow 
don't reach our citation threshold.

We agree that using "security" as a dimension
is misleading---we use it in the sense of "bypassability", which is 
orthogonal to "accuracy". We will replace it with a more specific term.

We agree about the minimalism of the security discussion, and
will try to enrich this part. For instance, approaches that provide
systematic arguments on why their designs are secure, aren't as
"bypassable" as heuristic/threshold-based approaches.

@@

Rev2:

The lack of code availability for most systems makes performing
original tests challenging, which is one of our findings, as we
explain in VII.B.

We attempt to equally cover every mechanism and then
highlight the reasons why a mechanism may be widely
used or not. In our conclusion section, we particularly mention
that CSP is one of the few that 
has been published and is widely used.
It is true that if programmers use
secure coding practices like prepared statements, then
SQLi protections aren't required.
However, best programming practices aren't always followed,
and this motivates proposals like SQLrand,
which might be easier to retrofit in existing code bases.

Our model covers attacks that utilize DSL languages in
general, and in our categorization there are more than
one countermeasures that protect from XPathi.

@@

Rev3:

Of course sensitivity and specificity could be expressed in terms of a
conditional probability---we will include this in the paper.

Our discussion in pages 2 and 13 highlights that we
cannot perform a set of measurements, calculate sensitivity and
specificity, and then using {True|False} {Positives|Negatives},
calculate PPV and NPV from equations 3 and 4 directly. One has to go
instead through equations 5 and 6.

We will expand on the advantages of PPV and NPV. PPV and NPV answer
the question about trusting a detection result; however, it isn't
always possible to get data for them as we indicate in p.13.

The comment on the skewed data is valid. The validity of test data is
important independently of sensitivity and specificity. We don't know
in the papers we studied if test data were skewed. We do find,
though, that: more tests could have been performed (Table I and
VII.A) and the means to conduct tests should be made available to
third parties (Table II and VII.B).

@@

Rev4:

We don't intend to criticize the lack of testing
in etiological mechanisms. We attempt to 
explore why such mechanisms aren't widely used, and suggest
that this is one reason.

Regarding the comment about demanding prevalence, it may be unfair to
ask of researchers to provide PPV and NPV values for their mechanisms.
In p.13 we explore what this would require---we will elaborate
more.

### 2015-01-16 docs/rebuttal_merged.txt

We thank the reviewers for their insightful comments.

Some general points:

* We didn't consider mechanisms that haven't been presented in
research papers. We mention Caja due to its importance.

* Although some of the presented works use static/dynamic analysis, we
 don't consider that area (another paper covers it [14]), but
 focus only on protections against attacks that exploit such
 vulnerabilities.

* We will update our paper to address the issues indicated by the the
  reviewers, i.e. the title, the point where language protection
  mechanisms detect an attack, the "ease of use" dimension, the SQLi
  example, the fact that we fail to capture PHP injection in our
  model, the 1/1.1 notation in our model, and the code availability
  discussion.

@@

Rev1:

Sensitivity and specificity should be more widely applicable, but not
enough data is given in the publications (see VII.A). The usefulness
of such metrics in computer security has been advocated by others,
i.e. Pfleeger and Pfleeger (Analyzing Computer Security: A
Threat/Vulnerability/Countermeasure Approach, Prentice Hall, 2011);
we’ll add the citation.

There are too many N/As in Table II, but this actually highlights the
issues regarding code availability and accuracy testing.

We will include FlowFox and JSand, the paper presenting IFC in
WebKit's JavaScript Bytecode and discuss ADsafe etc. and Caja.
AdSentry, Contego, and JSFlow don't reach our citation threshold.

Using "security" as a dimension is misleading---we mean ease of
circunvention, which is orthogonal to "accuracy". We
will replace it with a more specific term.

We'll enrich the security discussion. For instance, approaches that
provide systematic arguments on why their designs are secure, cannot
be circumvented like heuristic/threshold-based approaches.

@@

Rev2:

The lack of code availability for most systems makes performing
original tests challenging, which is one of our findings (VII.B).

We attempt to cover mechanisms and then highlight reasons why a
mechanism may not be widely used. In the conclusions we mention that
CSP is one of the few that has been published and is widely used. It
is true that if programmers use secure coding practices like prepared
statements, then SQLi protections aren't required. However, that may
not happen, and this motivates proposals like SQLrand, which might be
easier to retrofit in existing code bases.

@@

Our model covers attacks that utilize DSL languages in general, and in
our categorization there are more than one countermeasures that
protect from XPathi.

Rev3:

Sensitivity and specificity could be expressed in terms of a
conditional probability---we will include this in the paper.

Pages 2 and 13 highlight that we cannot perform a set of measurements,
calculate sensitivity and specificity, and then using {True|False}
{Positives|Negatives}, calculate PPV and NPV from equations 3 and 4
directly. One has to go instead through equations 5 and 6.

@@

The comment on the skewed data is valid. We don't know in the papers
we studied if test data were skewed. We do find, though, that: more
tests could have been performed (Table I and VII.A) and the means to
conduct tests should be made available to third parties (Table II and
VII.B).

Rev4:

We don't intend to criticize the lack of testing in etiological
mechanisms. We attempt to explore why such mechanisms aren't widely
used, and suggest that this is one reason.

Regarding the comment about demanding prevalence, it may be unfair to
ask of researchers to provide PPV and NPV values for their mechanisms.
In p.13 we explore what this would require---we will elaborate.
